Versatile Robust Clustering of Ad Hoc Cognitive Radio Network

### 2016-03-16 journal-draft/bare_jrnl_comsoc.tex
put all the notations there, need cleaning

@@

\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \texttt{Nb}_i\cup i}V_j|$, which is the number of common channels of CR node $i$ and its neighbours.
$G_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
\end{itemize}
Individual connectivity degree $D_i$ and social connectivity degree $G_i$ together form the \textit{connectivity vector}.
Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is calculated and shown.	
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Connectivity graph and the connectivity vector $\{D_i, G_i\}$ on each node. The available channels sensed by each CR node are: $V_A=\{1,2,3,4,5,6,10\}, V_B=\{1,2,3,5,7\}, V_C=\{1,3,4,10\}, V_D=\{1,2,3,5\}, V_E=\{2,3,5,7\}, V_F=\{2,4,5,6,7\}, V_G=\{1,2,3,4,8\}, V_H=\{1,2,5,8\}$. Dashed lines indicates two end nodes are within transmission range of each other. Each edge is labelled by the number of common channels between the two ends.}
	\label{fig1}
\end{figure}

@@

Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $V_C$ (the set of available channels in $C$), $V_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $V_C$, $V_{H_C}$, $|C|$, where $C\in S_i$.

@@

Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
Based on certain correlation, certain secondary users constitute one cluster $C$.
$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $V_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.

Following condition distinguishes the centralized clustering problem discussed in this paper.
The number of common control channels is $|V_{C}|$ if $|V_{C}|>1$, and is zero when $|V_{C}|=1$.
We use $f$ to denoted this new number of CCCs. 
The question of this problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_j'\cap C_j =\emptyset$ for $C_j', C_j\in \mathcal{S}'$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |V_{C}|\cdot |C|$, the product of number of common channels and cluster size.
The decision version of centralized clustering in CRN is to ask whether exist $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
\end{mydef}

@@

%\begin{table}[hc]
%\centering
%\caption{Singalling overhead. Notations: $n$-number of CR nodes in CRN, $h$-number of cluster heads, $m$-number of debatable nodes, $c$-number of demanding clusters.}\label{tab_overhead}
%\begin{tabular}{|p{2.2 cm}|p{1.5 cm}|p{3.7 cm}|}
%\hline
% Scheme 					&   Number of transmissions 					& Content of message \\ \hline
% ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
%				& $ID_{H_C}$ and $V_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $V_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
% SOC 						&   $3*n$					& $\{V_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
% Centralized				&	$n$						& $\{C\}$         	\\ 
% \hline
%\end{tabular}
%\end{table}

\begin{center}
\begin{table*}[ht]
\caption{Singalling overhead.}\label{tab_overhead}
{\small
\hfill{}
\begin{tabular}{|L{2.2 cm}|C{2.8 cm}|C{3.15 cm}|C{6.6 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message 									\\ \hline
 ROSS-DGA, ROSS-x-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming clusters' new membership ($|C_i|$ bytes)}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-x-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $V_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
\end{tabular}
}
\hfill{}
\end{table*}
\end{center}
% centralized: $\mathcal{O}(D(s)+log N)$ + $\mathcal{O}(1+D(s)+log N)$

@@

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section*{Algorithm~\ref{alg_size_control_available_CCC}}
\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{ROSS phase I: cluster head guarantees the availability of CCC (use line 1) / cluster size control (use line 2)}          % give the algorithm a caption
\label{alg_size_control_available_CCC}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Cluster C, empty sets $\tau_1, \tau_2$}
\KwOut{Cluster C has at least one CCC, or satisfies the requirement on cluster size}
%\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
\textbf{while} $V_C =\emptyset$ \textbf{do}\\
\While{$|C|> \delta$}{
	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
	\eIf{$\exists$ only one $i\in C\setminus H_C$, $i = \argmin(|K_{H_C}\cap K_i|)$}{
			$C=C\setminus i$;
		}{
				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{H_C}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
		}

	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$}{
		$C=C\setminus i$;
		}{
			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} V_j|-|\cap_{j\in C} V_j|)$;\\
			$C=C\setminus i$, where $i = \argmin_{i\in \tau_1} \texttt{ID}_i $
			%$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$;
	}
}
\end{algorithm}

\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{Debatable node $i$ decides its affiliation in phase II of ROSS}
%, chooses one claiming cluster to stay and leaves all the other claiming clusters}          % give the algorithm a caption,  cluster to settle
\label{alg4}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{all claiming clusters $C\in S_i$}
\KwOut{one cluster $C\in S_i$, node $i$ notifies all its claiming clusters in $S_i$ about its affiliation decision.
}
\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K_{C'\setminus i}|-|K_{C'}|<|K_{C\setminus i}|-|K_{C}|$}{
	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K_{C\setminus i}| - |K_C|)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K_{C\setminus i}| - |K_C|)$;\\ 
				$\tau_1\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(V_{H_C}\cap V_i)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(V_{H_C}\cap V_i)$;\\ 
				$\tau_2\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_2$, $C = \argmin|C|)$}{
			return $C$;
		}{
				return $\argmin_{C\in \tau_2}\texttt{ID}_{H_C}$;\\
		}
		}
\end{algorithm}

>>>>

xxxxxx

\begin{table}[h!]
\caption{Notations in robust clustering problem}
\label{tab1}
\centering
\begin{tabular}{llr}
\toprule
%\multicolumn{2}{c}{Item} \\
%\cmidrule(r){1-2}
Symbol & Description \\
\midrule
$\mathcal{N}$  & collection of secondary users\\
$N(i)$ & neighborhood of node $i$    \\
$K(i)$ & a cluster whose cluster head is $i$  \\
$C(i)$   & set of available channels at CR node $i$  \\
$C(K)$   & set of available CCCs of cluster $K$ \\
$C(K(i))$   & set of available CCCs of cluster $K(i)$ \\
$C_{K_i}$   & set of available CCCs of cluster $K(i)$ \\
$h(K)$ & cluster head of a cluster $K$\\
$h_K$ & cluster head of a cluster $K$\\
$\delta$ & desired cluster size\\
$S(i)$ & set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\

$\mathcal{N}$  & collection of secondary users\\
$N_i$ & neighborhood of node $i$    \\
$C_i$ & a cluster whose cluster head is $i$  \\
$K_i$   & set of available channels at CR node $i$  \\
$K_C$   & set of available CCCs of cluster $C$ \\
$K_{C_i}$   & set of available CCCs of cluster $C_i$ \\
$h_C$ & cluster head of a cluster $C$\\
$\delta$ & desired cluster size\\
$S_i$ & set of claiming clusters, each of which includes \\
& debatable node $i$ after phase I\\
\bottomrule
\end{tabular}
\end{table}

xxxxx

@@

\item \textit{Social connectivity degree} $G_i$: $G_i=|\bigcap_{j\in \texttt{Nb}_i\cup i}V_j|$, which is the number of common channels of CR node $i$ and its neighbours.
$G_i$ represents the ability of $i$ to form a robust cluster with its neighborhood.
\end{itemize}
Individual connectivity degree $D_i$ and social connectivity degree $G_i$ together form the \textit{connectivity vector}.
Figure~\ref{fig1} illustrates an example CRN where each node's connectivity vector is calculated and shown.	
\begin{figure}[ht!]
  \centering
\includegraphics[width=0.7\linewidth]{figure1.pdf}
% \includegraphics{figure1.pdf}
	\caption{Connectivity graph and the connectivity vector $(D_i, G_i)$ on each node. The available channels sensed by each CR node are: $K_A=\{1,2,3,4,5,6,10\}, K_B=\{1,2,3,5,7\}, K_C=\{1,3,4,10\}, K_D=\{1,2,3,5\}, K_E=\{2,3,5,7\}, K_F=\{2,4,5,6,7\}, K_G=\{1,2,3,4,8\}, K_H=\{1,2,5,8\}$. Dashed lines indicates two end nodes are within transmission range of each other. Each edge is labelled by the number of common channels between the two ends.}
	\label{fig1}
\end{figure}

@@

Algorithm for debatable node $i$ to decide which claiming cluster to stay is described as Algorithm~\ref{alg4}.
To conduct Algorithm~\ref{alg4}, debatable node $i$ needs to know the necessary information about its claiming clusters, \ie $K_C$ (the set of available channels in $C$), $K_{H_C}$ (the set of available channels on $C$'s cluster head $H_C$) and $|C|, C\in S_i$ (sizes of $i$'s claiming clusters).
After deciding which cluster to stay based on Algorithm~\ref{alg4}, node $i$ notifies all its claiming clusters, and retrieves the updated information of the necessary information $K_C$, $K_{H_C}$, $|C|$, where $C\in S_i$.

@@

Given a cognitive radio network $\mathcal{N}$ where nodes are indexed from 1 to $N$ sequentially.
Based on certain correlation, certain secondary users constitute one cluster $C$.
$1\leq |C| \leqslant k$ where $|C|$ is the size of cluster $C$ and $k$ is a positive integer.
We name the collection of such clusters as $\mathcal{S}=\{C_1, C_2,\ldots,C_{|\mathcal{S}|}\}$ (the subscript $i$ is the unique index of cluster in $\mathcal{S}$, not the ID of cluster head of that cluster), $\mathcal{S}$ satisfies the following properties: $\bigcup_{1\leq i \leq |\mathcal{S}|} C_i = N$ and $K_{C_i}\neq \emptyset$ for any $i$ which satisfies $1\leq i \leq |\mathcal{S}|$.

Following condition distinguishes the centralized clustering problem discussed in this paper.
The number of common control channels is $|K_{C}|$ if $|K_{C}|>1$, and is zero when $|K_{C}|=1$.
We use $f$ to denoted this new number of CCCs. 
The question of this problem is to find a subcollection $\mathcal{S}' \subseteq \mathcal{S}$, so that $\bigcup_{C_j\in \mathcal{S}'} C_j = N$, and $C_j'\cap C_j =\emptyset$ for $C_j', C_j\in \mathcal{S}'$, so that $\sum_{C\in \mathcal{S}'} f$ is maximized.
% when $|C|>1$, and $f(\cdot)=0$ when $|C|=1$.
%As to $f(\cdot):z\rightarrow z$, under this problem setting, if only number of common channels are given consideration, only singleton clusters will be preferred, which contradicts to our goal of clustering CR nodes together, thus we choose $f(\cdot)= |K_{C}|\cdot |C|$, the product of number of common channels and cluster size.
The decision version of centralized clustering in CRN is to ask whether exist $\mathcal{S}'\subseteq \mathcal{S}$, so that $\sum_{C\in \mathcal{S}'} f \geqslant \lambda$ where $\lambda$ is a real number.% in stead of to maximize $\sum_{C\in \mathcal{S}'} f$.
\end{mydef}

@@

%\begin{table}[hc]
%\centering
%\caption{Singalling overhead. Notations: $n$-number of CR nodes in CRN, $h$-number of cluster heads, $m$-number of debatable nodes, $c$-number of demanding clusters.}\label{tab_overhead}
%\begin{tabular}{|p{2.2 cm}|p{1.5 cm}|p{3.7 cm}|}
%\hline
% Scheme 					&   Number of transmissions 					& Content of message \\ \hline
% ROSS-DGA, ROSS-x-DGA 		&   $h+2*m^2c$ (upper bound)
%				& $ID_{H_C}$ and $K_C$ for $h+m^2c$ times, notification to join in one cluster for $m^2c$ times					\\ \hline
% ROSS-DFA, ROSS-x-DFA 		&   $h+ 2m$	 (upper bound) 						& $ID_{H_C}$ and $K_C$ for $h+m$ times, notification to join in one cluster for $m$ times	 					\\ \hline
% SOC 						&   $3*n$					& $\{K_i\}, i\in M\subseteq \texttt{Nb}_i$						\\ \hline
% Centralized				&	$n$						& $\{C\}$         	\\ 
% \hline
%\end{tabular}
%\end{table}

\begin{center}
\begin{table*}[ht]
\caption{Singalling overhead.}\label{tab_overhead}
{\small
\hfill{}
\begin{tabular}{|L{2.2 cm}|C{2.8 cm}|C{3.15 cm}|C{6.6 cm}|}
\hline
 Scheme 				&Message Complexity 	&   Quantitative number of messages 		& Content of message 									\\ \hline
 ROSS-DGA, ROSS-x-DGA 	&$\mathcal{O}(N^3)$ (worst case)		&   $h+2*m^2d$ (upper bound)  				&   \multirow{2}{*}{\parbox{6.4cm}{Phase I: notification from cluster head (1 byte), new individual connectivity degree (1 byte);  Phase II: update of debatable nodes' affiliation (1 byte), claiming clusters' new membership ($|C_i|$ bytes)}}								\\ \cline{1-3}
 ROSS-DFA, ROSS-x-DFA 	&$\mathcal{O}(N)$ (worst case)		&   $h + 2m$	 (upper bound) 					& 	      												\\ \hline
 SOC 					&$\mathcal{O}(N)$		&   $3*N$									& $C_i$ ($|C_i|$ bytes), $K_i$ ($P$ bytes), $i\in \mathcal{N}$						\\ \hline
 Centralized			&$\mathcal{O}(N)$			&	$h + m + N$ (upper bound)~\cite{Efficient_broadcasting_gathering_adhoc}		& $\{C\}$ ($|C_i|*N$ bytes)        					\\ \hline
\end{tabular}
}
\hfill{}
\end{table*}
\end{center}
% centralized: $\mathcal{O}(D(s)+log N)$ + $\mathcal{O}(1+D(s)+log N)$

@@

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
%\section*{Algorithm~\ref{alg_size_control_available_CCC}}
\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{ROSS phase I: cluster head guarantees the availability of CCC (use line 1) / cluster size control (use line 2)}          % give the algorithm a caption
\label{alg_size_control_available_CCC}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{Cluster C, empty sets $\tau_1, \tau_2$}
\KwOut{Cluster C has at least one CCC, or satisfies the requirement on cluster size}
%\tcc*[r]{When to guarantee available CCCs, execute from line 1, when to control cluster size, execute from line 2}
\textbf{while} $K_C =\emptyset$ \textbf{do}\\
\While{$|C|> \delta$}{
	%calculate $\lambda = \min_{i\in C, i\neq H_C}(|K_{H_C}\cap K_i|)$;\\
	\eIf{$\exists$ only one $i\in C\setminus H_C$, $i = \argmin(|K_{H_C}\cap K_i|)$}{
			$C=C\setminus i$;
		}{
				$\exists$ multiple $i$ which satisfies $i = \argmin(|K_{H_C}\cap K_i|)$;\\ $\tau_1\leftarrow i$;		
		}

	\eIf{$\exists$ only one $i\in \tau_1$, $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$}{
		$C=C\setminus i$;
		}{
			%$\exists$ multiple $i$ which satisfies $i = \argmax(|\cap_{j\in C\setminus i} K_j|-|\cap_{j\in C} K_j|)$;\\
			$C=C\setminus i$, where $i = \argmin_{i\in \tau_1} \texttt{ID}_i $
			%$\texttt{ID}_i$ is smaller than any $\texttt{ID}_j$, $j\in \tau_2\setminus i$;
	}
}
\end{algorithm}

\section*{}
\begin{algorithm}               % enter the algorithm environment
\caption{Debatable node $i$ decides its affiliation in phase II of ROSS}
%, chooses one claiming cluster to stay and leaves all the other claiming clusters}          % give the algorithm a caption,  cluster to settle
\label{alg4}
\DontPrintSemicolon
\SetAlgoLined
\KwIn{all claiming clusters $C\in S_i$}
\KwOut{one cluster $C\in S_i$, node $i$ notifies all its claiming clusters in $S_i$ about its affiliation decision.
}
\While{$i$ has not chosen the cluster, or $i$ has joined cluster $\tilde{C}$, but $\exists C'\in S_i, C'\neq \tilde{C}$, which has $|K_{C'\setminus i}|-|K_{C'}|<|K_{C\setminus i}|-|K_{C}|$}{
	\eIf{$\exists$ only one $C\in S_i$, $C = \argmin(|K_{C\setminus i}| - |K_C|)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmin(|K_{C\setminus i}| - |K_C|)$;\\ 
				$\tau_1\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_1$, $C = \argmax(K_{H_C}\cap K_i)$}{
			return $C$;
		}{
				$\exists$ multiple $C\in S_i$ which satisfies $C = \argmax(K_{H_C}\cap K_i)$;\\ 
				$\tau_2\leftarrow C$;		
		}
	\eIf{$\exists$ only one $C\in \tau_2$, $C = \argmin|C|)$}{
			return $C$;
		}{
				return $\argmin_{C\in \tau_2}\texttt{ID}_{H_C}$;\\
		}
		}
\end{algorithm}
